Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-11-26 ms.tex
updated ideal photodioide fig clarity and colors.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
The green and blue regions depict the N-type and P-type semiconductors.
The undepleted zones of the semiconductor (bright green and dark blue) contain mobile charge carriers whereas the depletion region (dark green) have no mobile carriers and all electrons are in the valence state.
The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
The voltage can be measured non-destructively as the well fills and then reset before saturating.}\label{fig:npSchematic}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
The green and blue regions depict the N-type and P-type semiconductors.
The undepleted zones of the semiconductor (fire brick and dim gray colors) contain mobile charge carriers whereas the depletion region (dark salmon) has no mobile carriers and all electrons are in the valence state.
The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
The voltage can be measured non-destructively as the well fills and then reset before saturating.}\label{fig:npSchematic}
\end{figure}
